Outbreak Threshold Detection

### 2023-03-09 notebooks/Julia/simulation-detection.qmd
Update dependency graph - doesn't work as produces too many jumps and exploding pop Look into using unbounded VariableJump that doesn't require specifying the dependency graph

```{julia}
x = 0:0.1:10
# 0.5 .* (sin.(2π .* x) .+ 1)
fig = lines(x, 0.5 .* (sin.(pi .* x ./ 2) .+ 1))
vlines!(collect(0:1:10); color = (:red, 0.5), linestyle = :dash)
fig
```

@@

# We require that rate1(u,p,s) <= urate(u,p,s)
# for t <= s <= t + rateinterval(u,p,t)
rateinterval(u, p, t) = typemax(t)
urate(u, p, t) = p[1] * u[1] * u[2]/ (u[1] + u[2] + u[3] + u[4])

# Optionally, we can give a lower bound over the same interval.
# This may boost computational performance.
lrate(u, p, t) = p[1] * u[1] * u[2]/ (u[1] + u[2] + u[3] + u[4])

@@

```{julia}
# Constant jumps are ordered ahead of VariableJumps, but otherwise retain the ordering
dep_graph = [
    [1], [2], [3], [4], [5], [6], [7],
    [1, 2, 3, 4, 5, 6, 7, 8] # Exposure jump
    ]

@@

```{julia}
out_jump = run_sir_sim(u₀ = u₀, tspan = tspan, p = p)
Array(out_jump)
```

>>>>

```{julia}
x = 0:0.1:10
fig = lines(x, 0.5 .* (sin.(2pi .* x) .+ 1))
vlines!(collect(0:1:10); color = (:red, 0.5), linestyle = :dash)
fig
```

@@

# We require that rate1(u,p,s) <= urate(u,p,s)
# for t <= s <= t + rateinterval(u,p,t)
urate(u, p, t) = p[1] * u[1] * u[2]/ (u[1] + u[2] + u[3] + u[4]) 
# Optionally, we can give a lower bound over the same interval.
# This may boost computational performance.
lrate(u, p, t) = 0

# rateinterval needs to be between lrate <= ri <= urate
rateinterval(u, p, t) = 1 / (2 * urate(u, p, t))

@@

```{julia}
# Constant jumps are ordered ahead of VariableJumps, but otherwise retain the ordering
dep_graph = [
    [1, 8],    # infec depends on states changed by itself and exposure jump
    [2],    # recov depends on states changed by itself
    [3],    # birth depends on states changed by itself
    [4, 8],    # S_death depends on states changed by itself and exposure jump
    [5, 8],    # E_death depends on states changed by itself and exposure jump
    [6],    # I_death depends on states changed by itself
    [7],    # R_death depends on states changed by itself and exposure jump
    [1, 3, 4, 5, 8]    # Exposure jump depends on states changed by itself, birth, S_death, E_death, and infection jumps
    ]

@@
